On Sample Size Needed for Block Bootstrap Confidence Intervals to Have Desired Coverage Rates

### 2023-08-26 Manuscript/manuscript.tex
Update, not finished

\subsection*{Design}
We designed a simulation study to compare the performance of the different block 
bootstrap CI methods. In particular, we generated time series $X_t$ from a 1st 
order auto-regressive (AR(1)) process:
\begin{equation}
X_t = \phi X_{t-1} + \epsilon_t,
\end{equation}
where $\phi$ is an auto-regressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. The 
series $X_t$ has mean zero and variance 
$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we 
set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
3) $\phi$, the lag-1 auto-correlation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
10000 replicates. For each replicate, we constructed six 95\% block bootstrap 
CIs for each parameter as described in the last section. We can estimate $\mu$, 
$\sigma_x$, and $\phi$ by computing the sample mean, sample standard deviation, 
and lag-1 auto-correlation, respectively, of each bootstrap sample. Then we can 
construct intervals for each parameter using the appropriate procedures 
described in \textit{Block Bootstrap CIs}. Then we estimated their actual coverage 
rates along with their 95\% confidence intervals from the 10000 replicates. The 
block bootstrap sampling step was done with function \texttt{tsboot} from R 
package \textsl{boot} \citep{boot}, with block size $\lceil n / l \rceil$. This 
function by default is an implementation of moving block bootstrap as described 
in the previous section, meaning that that blocks are allowed to wrap around, 
and $l = \lceil n^{1/3} \rceil$.

@@

\jy{The fonts of labels/annotatios in these figures are too big compared to the
  captions. Try pointsize = 9. The plots also seem oversized. Generate them in R
  with the right size in mind.}

@@

For estimating the auto-correlation parameter~$\phi$, 
\textbf{Figure~\ref{fig:phi}} suggests that while standard, Student's $t$, and 
recentered percentile CIs do approach correct coverage as sample size increases, 
percentile, BC, and BCA CIs deteriorate as sample size increases, especially as 
the strength of the temporal dependence increases. Because of this, only 
standard, Student's $t$, and recentered percentile CIs should be considered as 
effective block bootstrap methods to estimate $\phi$. Student's $t$ CIs once 
again can achieve correct coverage with smaller sample sizes when compared to 
standard and recentered percentile CIs which perform similarly. Student's $t$ 
CIs can can recover $\phi$ at the nominal level for $n \geq 100$ when the 
sample's temporal dependence is as strong as 0.4. Coverage appears to be higher 
for all methods when the dependence is negative rather than positive. Whether or 
not the dependence is negative or positive, coverage of $\phi$ seems to increase 
slightly as the absolute value increases for standard, Student's $t$, and 
recentered percentile CIs. For the values of $\phi$ observed, there are no 
examples of over-coverage for standard, Student's $t$, BC, BCA, or recentered 
percentile CIs. However, percentile CIs appear to over-cover $\phi$ for smaller 
sample sizes when $\phi = -0.2$ and when $\phi = 0$, indicating again that they 
should not be used.

@@

@@

\section{Simulation Study with Exponential Marginal Distribution}

@@

>>>>

\subsection*{Design}
We designed a simulation study to compare the performance of the different block 
bootstrap CI methods. In particular, we generated time series $X_t$ from a 1st 
order autoregressive (AR(1)) process:
\begin{equation}
X_t = \phi X_{t-1} + \epsilon_t,
\end{equation}
where $\phi$ is an autoregressive coefficient, and $\epsilon_t$ is a series of
independent errors from a normal distribution with mean zero and variance
$\sigma_{\epsilon}^2$. The strength of the serial dependence is controlled by
$\phi$, which was set to five levels: $\{-0.4, -0.2, 0.0, 0.2, 0.4\}$. The 
series $X_t$ has mean zero and variance 
$\sigma_x^2 = (1 - \phi^2) \sigma_{\epsilon}^2$, so for each value of $\phi$, we 
set $\sigma_{\epsilon}^2 = 1 / (1 - \phi^2)$ such that $\sigma_x^2 = 1$.

Three target parameters of $X_t$ were considered:
1) $\mu = 0$, the mean of $X_t$;
2) $\sigma_x = 1$, the standard deviation of $X_t$; and
3) $\phi$, the lag-1 autocorrelation coefficient.
To investigate the effect of sample size~$n$, we considered an array of values
$n \in \{100, 200, 400, 800, 1600, 3200\}$. In each configuration, we generated 
10000 replicates. For each replicate, we constructed six 95\% block bootstrap 
CIs for each parameter as described in the last section. We can estimate $\mu$, 
$\sigma_x$, and $\phi$ by computing the sample mean, sample standard deviation, 
and lag-1 autocorrelation, respectively, of each bootstrap sample. Then we can 
construct intervals for each parameter using the appropriate procedures 
described in \textit{Block Bootstrap CIs}. Then we estimated their actual coverage 
rates along with their 95\% confidence intervals from the 10000 replicates. The 
block bootstrap sampling step was done with function \texttt{tsboot} from R 
package \textsl{boot} \citep{boot}, with block size $\lceil n / l \rceil$. This 
function by default is an implementation of moving block bootstrap as described 
in the previous section, meaning that that blocks are allowed to wrap around, 
and $l = \lceil n^{1/3} \rceil$.

@@

\jy{The fonts of labels/annotatios in these figures are too big compared to the
  captions. Try pointsize = 9. The plots also seem oversized. Generate them in R
  with the right size in mind.} \mc{addressed}

@@

For estimating the autocorrelation parameter~$\phi$, 
\textbf{Figure~\ref{fig:phi}} suggests that while standard, Student's $t$, and 
recentered percentile CIs do approach correct coverage as sample size increases, 
percentile, BC, and BCA CIs deteriorate as sample size increases, especially as 
the strength of the temporal dependence increases. Because of this, only 
standard, Student's $t$, and recentered percentile CIs should be considered as 
effective block bootstrap methods to estimate $\phi$. Student's $t$ CIs once 
again can achieve correct coverage with smaller sample sizes when compared to 
standard and recentered percentile CIs which perform similarly. Student's $t$ 
CIs can can recover $\phi$ at the nominal level for $n \geq 100$ when the 
sample's temporal dependence is as strong as 0.4. Coverage appears to be higher 
for all methods when the dependence is negative rather than positive. Whether or 
not the dependence is negative or positive, coverage of $\phi$ seems to increase 
slightly as the absolute value increases for standard, Student's $t$, and 
recentered percentile CIs. For the values of $\phi$ observed, there are no 
examples of over-coverage for standard, Student's $t$, BC, BCA, or recentered 
percentile CIs. However, percentile CIs appear to over-cover $\phi$ for smaller 
sample sizes when $\phi = -0.2$ and when $\phi = 0$, indicating again that they 
should not be used.

@@

An additional simulation study in which block bootstrap is used to estimate 
parameters of an AR(1) process with an underlying exponential marginal 
distribution is discussed in the appendix.

@@

\section*{Simulation Study with Exponential Marginal Distribution}

@@

This appendix concerns the performance of block bootstrap when used to estimate
the mean, standard deviation, and the lag-1 autocorrelation coefficient of a 
AR(1) process with an underlying exponential marginal distribution. The 
motivation for this additional simulation study was to observe if the results of 
the main simulation study will change if the underlying marginal distribution is
not normal. The data
